%%% he main file. It contains definitions of basic parameters and includes all other parts.

%% Settings for single-side (simplex) printing
% Margins: left 40mm, right 25mm, top and bottom 25mm
% (but beware, LaTeX adds 1in implicitly)
%\documentclass[12pt,a4paper]{report}
%\setlength\textwidth{145mm}
%\setlength\textheight{247mm}
%\setlength\oddsidemargin{15mm}
%\setlength\evensidemargin{15mm}
%\setlength\topmargin{0mm}
%\setlength\headsep{0mm}
%\setlength\headheight{0mm}
% \openright makes the following text appear on a right-hand page
%\let\openright=\clearpage

%% Settings for two-sided (duplex) printing
% urcite tiskni oboustranne, jednostranny bakalarky jsou fuj.
\documentclass[12pt,a4paper,twoside,openright]{report}
%
% btw haha, tady si ruzny matfyzaci mysleli ze umej typografii lip nez
% profesionalove co se tim zabejvaji poslednich 300 let. Kdyby ti prislo ze
% stranky jsou tedka "divne rozjety do stran", tak to je dobre a kazdej tiskar
% to pochvali. Pak nekdy kdyztak vysvetlim proc to tak je.
%
%\setlength\textwidth{145mm}
%\setlength\textheight{247mm}
%\setlength\oddsidemargin{14.2mm}
%\setlength\evensidemargin{0mm}
%\setlength\topmargin{0mm}
%\setlength\headsep{0mm}
%\setlength\headheight{0mm}
\let\openright=\cleardoublepage

%% Prefer Latin Modern fonts
\usepackage{lmodern}

%% Further useful packages (included in most LaTeX distributions)
\usepackage{amsmath}        % extensions for typesetting of math
\usepackage{amsfonts}       % math fonts
\usepackage{amsthm}         % theorems, definitions, etc.
\usepackage{bbding}         % various symbols (squares, asterisks, scissors, ...)
\usepackage{bm}             % boldface symbols (\bm)
\usepackage{bbm}
\usepackage{graphicx}       % embedding of pictures
\usepackage{fancyvrb}       % improved verbatim environment
\usepackage[numbers]{natbib} % citation style AUTHOR (YEAR), or AUTHOR [NUMBER]
\bibliographystyle{plainnat} % this must be moved here for natbib to work correctly
\usepackage[nottoc]{tocbibind} % makes sure that bibliography and the lists
			    % of figures/tables are included in the table
			    % of contents
\usepackage{dcolumn}        % improved alignment of table columns
\usepackage{booktabs}       % improved horizontal lines in tables
\usepackage{paralist}       % improved enumerate and itemize
\usepackage{multicol}
\usepackage{multirow, makecell}
% \usepackage[usenames]{xcolor}  % typesetting in color
\usepackage[table,dvipsnames,usenames,rgb]{xcolor}  % typesetting in color

\usepackage[hyphens,spaces,obeyspaces]{url}

\usepackage[textsize=tiny]{todonotes} %visual todo!

\usepackage{xspace}         %for......xspace.
\usepackage{fancyvrb}
\usepackage{rotating}
\usepackage{collcell}
\usepackage{nomencl}
\usepackage{siunitx}
\usepackage{listings}

% my packages
\usepackage{models}

\usepackage{pgfplots}
\pgfplotsset{compat=1.8}
\usepgfplotslibrary{statistics}


%% Generate PDF/A-2u
\usepackage[a-2u]{pdfx}

\usepackage{cleveref}       %\cref yay!

%% Character encoding: usually latin2, cp1250 or utf8:
\usepackage[utf8]{inputenc}

%%% Basic information on the thesis

% Thesis title in English (exactly as in the formal assignment)
\def\ThesisTitle{Object detection for video surveillance using the SSD approach}

% Author of the thesis
\def\ThesisAuthor{Marek Dobranský}

% Year when the thesis is submitted
\def\YearSubmitted{2019}

% Name of the department or institute, where the work was officially assigned
% (according to the Organizational Structure of MFF UK in English,
% or a full name of a department outside MFF)
\def\Department{Department of Software Engineering}

% Is it a department (katedra), or an institute (ústav)?
\def\DeptType{Department}

% Thesis supervisor: name, surname and titles
\def\Supervisor{RNDr. Jakub Lokoč, Ph.D.}

% Supervisor's department (again according to Organizational structure of MFF)
\def\SupervisorsDepartment{Department of Software Engineering}

% Study program and specialization
\def\StudyProgramme{Computer Science}
\def\StudyBranch{Artificial inteligence}

% An optional dedication: you can thank whomever you wish (your supervisor,
% consultant, a person who lent the software, etc.)
\def\Dedication{%
I would like to express my gratitude to RNDr. Jakub Lokoč, Ph.D., the supervisor of this thesis, for his patient guidance, feedback and all advice he has given me. 

I also want to thank my family and girlfriend for their continued support and encouragement during my studies and especially during the time spent working on this thesis.
}

% Abstract (recommended length around 80-200 words; this is not a copy of your thesis assignment!)
\def\Abstract{%
The surveillance cameras serve various purposes ranging from security to traffic monitoring and marketing. However, with the increasing quantity of utilized cameras, manual video monitoring has become too laborious. In recent years, a lot of development in artificial intelligence has been focused on processing the video data automatically and then outputting the desired notifications and statistics. This thesis studies the state-of-the-art deep learning models for object detection in a surveillance video and takes an in-depth look at SSD architecture. We aim to enhance the performance of SSD by updating its underlying feature extraction network. We propose to replace the initially used VGG model by a selection of modern ResNet, Xception and NASNet classification networks. The experiments show that the ResNet50 model offers the best trade-off between speed and precision, while significantly outperforming VGG. With a series of modifications, we improved the Xception model to match the ResNet performance. On top of the architecture-based improvements, we analyze the relationship between SSD and a number of detected classes and their selection. We also designed and implemented a new detector with the use of temporal context provided by the video frames. This detector delivers enhanced precision while meeting real-time requirements.
}

\def\AbstractSK{
Kamerové systémy dnes slouží různým účelům, od bezpečnosti k monitorování dopravy a marketingu. Nicméně, s rostoucím množstvím kamer se stává manuální sledování videa příliš pracné. V posledních letech se hodně vývoje umělé inteligence zaměřilo na automatické zpracování videa a následný výstup požadovaných upozornění a statistik. Tato práce zkoumá nejmodernější modely hlubokého učení pro detekci objektů v bezpečnostním videu a podrobně se zabývá SSD architekturou. Našim hlavním cílem je zvýšit výkon SSD architektury aktualizací vnitřní sítě extrahující tzv. feature mapy. V práci jsou navrženy vhodné možnosti nahrazení původního VGG modelu pomocí nejnovějších klasifikačních sítí ResNet, Xception a NASNet. Experimentálně jsme zjistili, že model ResNet50 nabízí nejlepší kompromis mezi rychlostí a přesností. Tento model zároveň výrazně překonává VGG. Po zavedení řady modifikací do sítě Xception se nám povedlo dorovnat výkon ResNetu. Kromě vylepšení architektury také analyzujeme vztah mezi SSD a množstvím detekovaných tříd a jejich výběrem. Také jsme navrhli a implementovali nový detektor, který využívá temporální kontext snímku pro detekci objektů. Tento detektor pracuje v reálném čase a se zvýšenou přesností.
}

% 3 to 5 keywords (recommended), each enclosed in curly braces
\def\Keywords{%
{object detection}, {video surveillance}, {deep neural networks}, {SSD architecture}
}

%% The hyperref package for clickable links in PDF and also for storing
%% metadata to PDF (including the table of contents).
%% Most settings are pre-set by the pdfx package.
\hypersetup{unicode}
\hypersetup{breaklinks=true}

% Definitions of macros (see description inside)
\include{utility/macros}

% Title page and various mandatory informational pages
\begin{document}
\include{utility/title}

%%% A page with automatically generated table of contents of the bachelor thesis
\tableofcontents
%%% Each chapter is kept in a separate file
\include{chapters/chap00}
\include{chapters/chap01}
\include{chapters/chap02}
\include{chapters/chap03}
\include{chapters/chap04}
\include{chapters/chap05}
\include{chapters/chap99}

%%% Bibliography
\include{bibliography}

\appendix
\include{chapters/chapA}


%%% Figures used in the thesis (consider if this is needed)
\listoffigures
% list of figures je dobrej do knizek co maj 500+ stranek, tady to je uplna zbytecnost.

%%% Tables used in the thesis (consider if this is needed)
%%% In mathematical theses, it could be better to move the list of tables to the beginning of the thesis.
%\listoftables

%%% Abbreviations used in the thesis, if any, including their explanation
%%% In mathematical theses, it could be better to move the list of abbreviations to the beginning of the thesis.
% \chapwithtoc{List of Abbreviations}
%%% Attachments to the bachelor thesis, if any. Each attachment must be
%%% referred to at least once from the text of the thesis. Attachments
%%% are numbered.
%%%
%%% The printed version should preferably contain attachments, which can be
%%% read (additional tables and charts, supplementary text, examples of
%%% program output, etc.). The electronic version is more suited for attachments
%%% which will likely be used in an electronic form rather than read (program
%%% source code, data files, interactive charts, etc.). Electronic attachments
%%% should be uploaded to SIS and optionally also included in the thesis on a~CD/DVD.
%%% Allowed file formats are specified in provision of the rector no. 23/2016.
%\chapwithtoc{Attachments}

\openright
\end{document}
